Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-04 robdml.tex
sec2

%
\textbf{Defenses in DML.} Compared to attacks, defense methods for DML are less
explored.
%
Zhou \etal~\cite{advrank} present Embedding Shifted Triplet (EST), an
adversarial training method using adversarial examples with maximized embedding
move distance off their original locations.
%
Anti-Collapse Triplet (ACT)~\cite{robrank} forces the model to separate
collapsed positive and negative samples in order to learn robust features,
which achieves the state-of-the-art robustness.
%
However, the existing defense methods suffer from low efficiency as a
relatively weak adversary is used in order to avoid model collapse.

>>>>

%
\textbf{Defenses in DML.} Different from attacks, defense methods are less
explored.
%
Embedding Shifted Triplet (EST)~\cite{advrank} is an
adversarial training method using adversarial examples with maximized embedding
move distance off their original locations.
%
Anti-Collapse Triplet (ACT)~\cite{robrank} forces the model to separate
collapsed positive and negative samples apart in order to learn robust
features, which achieves the state-of-the-art robustness.
%
However, the existing defense methods suffer from low efficiency as the
inner problem is replaced into a indirect form in order to avoid model collapse.
